### 2020-10-09 input/background.tex
removal of partition figure

When $distance$ involves monotonically increasing scalars such as
latency or number of hops between sources and processes, the optimal
partitioning consists in processing the multiple destinations shortest
path~\REF at each process.  Algorithm~\ref{algo:add} shows the
instructions of such dynamic partitioning where the only operation
available to processes is the adding of a
partition. Figure~\ref{fig:add} illustrates its behavior on a system
comprising 4 processes $a$, $b$, $c$, and $d$. Two processes $a$ and
$c$ concurrently create a partition. They initialize their own state
with the lowest possible bound $0$ (see Line~\ref{line:lowestbound}),
and send a message to each of their neighbors by accumulating the
corresponding edge weight (see Line~\ref{line:accumulator}). In
Figure~\ref{fig:addC}, Process $b$ receives $Add_{c, 1}$. Since it
improves its own partition distance, it keeps it and forwards it to
its neighbors. Process $b$ discards $Add_{b, 1.5}$, for it does not
improve its partition distance. Processes $c$ and $d$ will never hear
of Process $a$'s partition. In Figure~\ref{fig:addD}, processes
discard last transiting messages. The system converged to the optimal
partitioning.

@@

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
      Process $c$ initiate then remove a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:delB}\TODO{mew}.]{\input{input/figdelB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:delC}\TODO{mew}.]{\input{input/figdelC.tex}}
    \hspace{5pt}

  \end{center}
  \caption{\label{algo:add}Removing partition may lead to inconsistent states.}
\end{figure*}

>>>>

When $distance$ involves monotonically increasing scalars such as
latency or number of hops between sources and processes, the optimal
partitioning consists in processing the multiple destinations shortest
path~\REF at each process.  Algorithm~\ref{algo:add} shows the
instructions of such dynamic partitioning where the only operation
available to processes is the adding of a
partition. Figure~\ref{fig:add} illustrates its behavior on a system
comprising 4 processes $a$, $b$, $c$, and $d$. Two processes $a$ and
$c$ concurrently create a partition. They initialize their own state
with the lowest possible bound $0$ (see Line~\ref{line:lowestbound}),
and send a message to each of their neighbors by accumulating the
corresponding edge weight (see Line~\ref{line:accumulator}). In
Figure~\ref{fig:addC}, Process $b$ receives $Add_{c, 1}$. Since it
improves its own partition distance, it keeps it and forwards it to
its neighbors. Process $b$ discards $Add_{b, 1.5}$, for it does not
improve its partition distance. Processes $c$ and $d$ will never hear
of Process $a$'s partition. \TODO{At scale.} In Figure~\ref{fig:addD},
processes discard last transiting messages. The system converged to
the optimal partitioning.

@@

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
      Process $c$ initiate then remove a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:delB}Process $b$ and Process $d$ receive and deliver
      messages based on their weights. $a$'s partition propagates to all processes.]
             {\input{input/figdelB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:delC}Process $c$'s partition reach $b$ and $d$.
      Its removal shortly follows. Process $b$ does not have any control
      information about partitions any more.]{\input{input/figdelC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:delD}Processes discard remaining messages.
      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
      partition.]{\input{input/figdelD.tex}}
  \end{center}
  \caption{\label{algo:add}Removing partition may lead to inconsistent states.}
\end{figure*}

### 2020-10-09 input/figdelA.tex
removal of partition figure

  \newcommand\ADD{Add}
  \newcommand\DEL{Del}

  \draw (-\X, 0) -- node[above,font=\tiny]{$\ADD_{a, 1.5}$} (0, 0); %% a - b
  \draw (0, 0) -- node[above, font=\tiny]{$\ADD_{c, 1}$} (\X, 0); %% b - c
  \draw (0, 0) -- (0, \Y); %% b - d
  \draw (\X, 0) -- node[below, font=\tiny, sloped]{$\ADD_{c, 1}$} (0, \Y); %% c - d

@@

  \draw (-\X+5pt, 5pt) node[above left]{$\DEL_a$};
  \draw (\X+5pt, 5pt) node[above right]{$\DEL_c$};

>>>>

  \newcommand\ADD{\alpha}
  \newcommand\DEL{\delta}

  \draw[->] (-\X + 5pt, 0 + 2pt ) --
  node[above=-0.3em,font=\tiny]{$\ADD_{a}^{1.5}$}
  (0 - 5pt, 0 + 2pt); %% a - b
  \draw[<-] (-\X + 5pt, 0 - 2pt ) --
  (0 - 5pt, 0 - 2pt); %% b - a

  \draw[<-] (0 +5pt, 0 + 2pt) --
  node[above=-0.3em, font=\tiny]{$\ADD_{c}^{1}$}
  (\X -5pt, 0 + 2pt); %% c - b
  \draw[->] (0 +5pt, 0 - 2pt) --
  (\X -5pt, 0 - 2pt); %% b - c

  \draw[->] (0 + 2pt, 0 - 5pt) --
  (0 + 2pt, \Y + 5pt); %% b - d
  \draw[->] (0 - 2pt, \Y + 5pt) --
  (0 - 2pt, 0 - 5pt);  %% d - b

  \draw[<-] (\X - 3pt, 0 - 5pt) --
  (0 + 5pt, \Y + 3pt); %% d - c
  \draw[->] (\X + 3pt, 0 - 5pt) --
  node[below=-0.3em, font=\tiny, sloped]{$\ADD_{c}^{1}$}
  (0 + 5pt, \Y - 3pt); %% c - d

@@

  \draw (-\X, 5pt) node[above]{$\DEL_a$};
  \draw (\X, 5pt) node[above]{$\DEL_c$};
